\cvsection{Additional experience}

\begin{cventries}
  \cventry
    {Top 10\% worldwide} % subtitle
    {Google Hash Code} % organisation
    {} % location
    {} % date
    {
      \begin{cvitems} % description
        \item {Led a team of 4 people in engineering two systems: one to assign passengers to autonomous vehicles, another to distribute autonomous vehicles to different locations in order to preempt passenger demand.}
        \vspace{0.5mm}
        \item {Iterated over the basic algorithms to specialise for different real-world scenarios, returning the optimal routes and starting locations for environments including a single metropolis, neighbouring cities, and cities separated by countryside.}
        \vspace{0.5mm}
        \item {Achieved first place within hub, top 10\% worldwide.}
      \end{cvitems}
    }
    
  \cventry
    {First place}
    {BAE Systems Applied Intelligence Capture the Flag}
    {}
    {}
    {
      \begin{cvitems}
        \item {Worked in a team of 5 to find exploits in a BAE designed system, specialising in reverse engineering and packet inspection.}
        \vspace{0.5mm}
        \item {Achieved first place out of twelve finalists.}
      \end{cvitems}
    }
    
  \cventry
    {Open source contributor}
    {Void Linux}
    {}
    {}
    {
      \begin{cvitems}
        \item {Package maintainer and contributor to the Void Linux project.}
        \vspace{0.5mm}
        \item {Used Bash, C and continuous integration (Travis CI) to develop and test both infrastructure and packages.}
      \end{cvitems}
    }
    
  \cventry
    {Director of Technology}
    {Nouse}
    {}
    {}
    {
      \begin{cvitems}
        \item {Developed the website and oversaw publishing of the university newspaper.}
        \vspace{0.5mm}
        \item {Maintained, upgraded and administered all servers and other hardware belonging to Nouse.}
      \end{cvitems}
    }

  \cventry
    {Treasurer}
    {University of York Mixed Martial Arts Club}
    {}
    {}
    {
      \begin{cvitems}
        \item {Managed club finances including memberships, sponsorships and grants.}
        \vspace{0.5mm}
        \item {Handled club interactions with external companies and third-party investors.}
      \end{cvitems}
    }
\end{cventries}